Portal Forecast

### 2018-03-16 index.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(portalr)
source("tools/forecast_tools.R")
source("tools/model_functions.R")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(portalr)
source("tools/forecast_tools.R")
source("tools/data_tools.R")
```
